---
title: "Ten simple rules for statistical analyses"
author:
  - Mark D. Scheuerell:
      email: scheuerl@uw.edu
      institute: wacfwru
      correspondence: true
  - name: Sarah J. Converse
    institute: wacfwru
institute:
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 2
fontsize: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "aslo.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

## load {knitcitations}
library("knitcitations")

## clean out any existing .bib files
# cleanbib()

## set pandoc for formatting
options("citation_format" = "pandoc")
```

\vspace{3.5in}

This draft manuscript is distributed solely for purposes of scientific peer review. Its content is deliberative and predecisional, so it must not be disclosed or released by reviewers. Because the manuscript has not yet been approved for publication by the U.S. Geological Survey (USGS), it does not represent any official USGS finding or policy.

\newpage

## Notes for Sarah & Mark

### Example

As an example, here is the first essay of this type for the journal:

https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1002/lol2.10165

### Generating references



`r citet("10.1002/lol2.10165")`

\newpage

# Rules for statistical analysis

\footnote{This is just a placeholder.}


# Conclusion


# Conflict of interest

The authors have no conflicts of interest.

# Acknowledgments


# References

```{r}
## create ref cited section
write.bibtex(file = "references.bib")
```


