---
title: "Ten simple rules for statistical analyses"
author:
  - Mark D. Scheuerell:
      email: scheuerl@uw.edu
      institute: wacfwru
      correspondence: true
  - name: Sarah J. Converse
    institute: wacfwru
institute:
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    highlight: haddock
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 1.1
fontsize: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "aslo.csl"
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

## load {knitcitations}
library("knitcitations")

## clean out any existing .bib files
# cleanbib()

## set pandoc for formatting
options("citation_format" = "pandoc")
```

\vspace{4in}

This draft manuscript is distributed solely for purposes of scientific peer review. Its content is deliberative and predecisional, so it must not be disclosed or released by reviewers. Because the manuscript has not yet been approved for publication by the U.S. Geological Survey (USGS), it does not represent any official USGS finding or policy.

\newpage

## Notes for Sarah & Mark

### Journal guidelines

Here is the information from the journal's [author guidelines](https://aslopubs.onlinelibrary.wiley.com/hub/journal/23782242/about/author-guidelines#Articletypes):

> Essays should include ideas, concepts, hypotheses, or opinions to stimulate discussion, debate or research. Essays can be written as opinion pieces that are well-reasoned with well-supported arguments and ideas, but where extensive citations are not needed or available. Essays should be written in clear and general language that are understandable to a broad audience.

> - 2,500 words maximum (includes main-body text only; excluding significance statement, acknowledgements, and references) and 1-3 visuals (figures, tables, or boxes).

> - Essays should include: Significance statement, text (sub-headings are optional), references. Note that essays do not include an abstract.

### Essay example

As an example, [here](https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1002/lol2.10165) is the first essay of this type for the journal.

### Generating references

There are a couple of ways to add references to the `references.bib` file. The first is to copy/paste them from any reference software that will display them in `.bib` format (e.g., EndNote, Zotero). For example,

```{r, eval = FALSE, echo = TRUE}
@Article{Smith_2021,
  year = {2021},
  publisher = {The Ecological Society of America},
  volume = {123},
  number = {2},
  pages = {1-10},
  author = {Jane Smith and Joe Johnson},
  title = {Probably the best paper ever written},
  journal = {Ecology},
}
```

The second is to use the `{knitcitations}` package, which will load when the `.Rmd` file is knit. Here is an example of an inline **`R`** command that will

1) create an entry in `references.bib` for Hotaling (2020) linked to above;
2) display a properly formatted citation in the text; and
3) add a formatted entry to the References section.

```{r eval = FALSE, echo = TRUE}
`r citet("10.1002/lol2.10165")`
```

`r citet("10.1002/lol2.10165")`

You can see other examples [here](https://fish497.github.io/website/lectures/week_07/lec_20_markdown_1.html#knitcitations_package).

\newpage

# Scientific significance statement

[ _This section and heading are required._ ]

For example, here's what Scott wrote in his essay:

> One of the most common editorial refrains, regardless of discipline, is “this needs to be tighter.” It typically means too many words and ideas are jumbled together and the underlying point is obscure. The writing is not concise. But, improving conciseness is difficult because the problem is caused by a host of factors that are easily overlooked, especially by early career researchers. Here, I describe what it means to write concisely and outline 10 rules, with examples, to help scientists tighten their prose.

# Introduction

[ _This section was 3 paragraphs in Scott's essay (and it lacked an actual heading)._ ]


# Rules for statistical analysis

[ _The above heading is just a placeholder._ ]

Here are some possible topics, ordered around the notions of before, during, and after a study/analysis, which we had discussed briefly.

## Before beginning

* Do not mix frequentist and Bayesian paradigms

    - We're not making a judgment call here, but merely pointing out that there are important philosophical differences that should not be confused/conflated.

* Consider acceptable levels of Type-I and Type-II errors

    - If frequentist, choose an $\alpha$-value ahead of time

## During analysis

* Model diagnostics are an important part of any analysis

    - Every model or test involves assumptions; are they met?


## Reporting (after)

* Effect size is more important than a p-value

    - Highly replicated experiments have large power to detect differences/effect, but are they meaningful?

* Model selection exercises will always find a "best" model

    - Model selection via in-sample (eg, AIC) or out-of-sample (eg, LOO) will identify a best model, but the question is how good is it?
    

# Conclusion

[ _The above heading is just a placeholder and is not actually necessary._ ]


# Conflict of interest

The authors have no conflicts of interest.


# Acknowledgments

We wish to thank...


\newpage

# References

\setlength{\parindent}{-0.375in}
\setlength{\leftskip}{0.375in}
\setlength{\parskip}{8pt}
\noindent

```{r}
## create ref cited section
write.bibtex(file = "references.bib")
```


